\sysfull

### 2018-04-16 paper/evaluation.tex

%Then, we need to know how many tasks \sys can coalesce within a given execution scenario. We ran a subset of applications (split by tasks manually) with continuous power supply and measured the size of tasks for each application and the amount of tasks coalesced. Result is given in Table~\ref{tab:aveVirtuTaskSize}. We see clearly that \sys manages to coalesce more tasks as individual tasks are small. As the size of individual task increases, e.g., as in the case of dft application, the number of coalesced tasks is also small. This result clearly shows that for the benefit of coalescing and for code portability, initial code should be split by \emph{as small tasks as possible}. This will help \sys to find the best possible virtual task size to minimise its runtime.

@@

\textbf{\sys Kernel Overhead Breakdown.} We now proceed with investigating how much utilization \sys's kernel steals to user code, quantifying task transitions and memory accesses overhead. For a broader picture, we profile kernel load for NC as well. The result for all benchmarks are measured in the same way as for the results presented above (i.e. given in Figure~\ref{fig:overallOverheadBreakdown}) and using the same page sizes as in the previous experiment. The outcome is presented in Figure~\ref{fig:coalEfficiency} (left side).
%
As expected, non-coalescing (NC) \sys introduces a huge cost of task transitions and commits (which recapitulates the result presented in Figure~\ref{fig:overallOverheadBreakdown}). For both coalescing strategies (EA and ETA) protected variables' accesses constitutes about 30\% of the whole load across all benchmarks. In fact, dynamic address translation is the most critical bottleneck for \sys.

\textbf{Protected Memory Accesses Breakdown.} Figure~\ref{fig:coalEfficiency} (right side) zooms into the overhead introduced by \sys's protected memory accesses.
% Let us now look into the results on the \sys memory operation process, i.e. we will show specifically which parts of memory from Figure~\ref{fig:coalEfficiency} (left) are accessed. The result is presented in Figure~\ref{fig:coalEfficiency} (right).
We immediately see that the majority of operations are targeting the most recently accessed SRAM page, and very few operations include a page swap from FRAM. There are very few cases involving SRAM pages other than the last one (only visible for \textbf{cuckoo} and \textbf{dijkstra}). This distinction is important because, when searching the \texttt{\underline{working}} buffer, the most recently accessed page is the first one being checked by \sys. This choice is highly motivated by this result. It is important to mention that memory access patterns are fully shaped by the application, and those ones which use a lot of protected memory can generate a higher rate of page swaps.

@@

\textbf{\sys versus non-adaptive Task-based Model.} We now evaluate \sys's run time and compare it to Alpaca---a non-adaptive task-based system. Results are presented in Figure~\ref{fig:runtime}. For each application we measured its execution time using real wireless power provisioned by the RF signal generator at three distances (refer again to Section~\ref{sec:implementation}). The plot presents the average execution time of each application for Coala and Alpaca, normalized to the latter. The results show that \sys provides a performance benefit compared to Alpaca for most applications (all except for \textbf{ar} and \textbf{cuckoo} at 30 and 50\,cm). The improvement is the greatest for applications that perform repeated write after read operations, particularly if involving arrays (\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). This effect is seen at all distances on intermittent power. In applications with protected variables (or array elements) accessed next to each other, but residing in different SRAM or FRAM pages, \sys incurs overhead from memory virtualization that causes its performance to be comparable to (or worse than) Alpaca (\textbf{ar}, \textbf{cuckoo}).
%
Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys's task downscaling mechanism, which was intendedly disabled for this experiment, will be able to solve this issue.

\begin{wrapfigure}{t!}{0.5\textwidth}
%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP-to-exciter distances \{0.15, 0.3, 0.5\}\,m, compared against Alpaca (results normalized to Alpaca's performances) for ETA coalescing strategy. Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys is comparable with, or worse than, Alpaca.
	\label{fig:runtime}
%\end{figure}
\end{wrapfigure}

@@

\textbf{Effect of Page Size on Run Time.} The results (Figure~\ref{fig:page_size}, left) show a ``bathtub curve'' in the performance of each application (the effect would be more profound with a larger set of pages than we considered), as the number of page faults varies. The data suggest that across applications there is a page size that minimizes execution time. We observe that the page size is not the same for each application, although 128\,B pages perform well for all applications.

\textbf{Page Size versus Page Faults in \sys Runtime.} The increased rate of page faults (Figure~\ref{fig:page_size}, right) is responsible for the overhead with small page sizes; smaller pages require accessing more different pages, leading to higher paging costs. With larger page sizes, the overhead is higher than with moderate pages, too. The explanation for these higher overheads is that large pages have a higher commit cost. Even if an application accesses few memory locations, \sys pages data at full page size, degrading performance by sometimes paging in and out unnecessary data. The data reveal a reasonable default page size of 128\,B and, when developing an application, a programmer should consider varying the page size to moderate poor performance.

>>>>

@@

\textbf{\sys Kernel Overhead Breakdown.} We now proceed with investigating how much utilization \sys's kernel steals to user code, quantifying task transitions and memory accesses overhead. For a broader picture, we profile kernel load for NC as well. The result for all benchmarks are measured in the same way as for the results presented above (i.e. given in Figure~\ref{fig:overallOverheadBreakdown}) and using the same page sizes as in the previous experiment. The outcome is presented in Figure~\ref{fig:coalEfficiency} (left side). As expected, non-coalescing (NC) \sys introduces a huge cost of task transitions and commits (which recapitulates the result presented in Figure~\ref{fig:overallOverheadBreakdown}). For both coalescing strategies (EA and ETA) protected variables' accesses constitutes about 30\% of the whole load across all benchmarks. In fact, dynamic address translation is the most critical bottleneck for \sys.

\textbf{Protected Memory Accesses Breakdown.} Figure~\ref{fig:coalEfficiency} (right side) zooms into the overhead introduced by \sys's protected memory accesses. We immediately see that the majority of operations are targeting the most recently accessed SRAM page, and very few operations include a page swap from FRAM. There are very few cases involving SRAM pages other than the last one (only visible for \textbf{cuckoo} and \textbf{dijkstra}). This distinction is important because, when searching the \texttt{\underline{working}} buffer, the most recently accessed page is the first one being checked by \sys. This choice is highly motivated by this result. It is important to mention that memory access patterns are fully shaped by the application, and those ones which use a lot of protected memory can generate a higher rate of page swaps.

@@

\textbf{\sys versus non-adaptive Task-based Model.} We now evaluate \sys's run time and compare it to Alpaca---a non-adaptive task-based system. Results are presented in Figure~\ref{fig:runtime}. For each application we measured its execution time using real wireless power provisioned by the RF signal generator at three distances (refer again to Section~\ref{sec:implementation}). The plot presents the average execution time of each application for Coala and Alpaca, normalized to the latter. The results show that \sys provides a performance benefit compared to Alpaca for most applications (all except for \textbf{ar} and \textbf{cuckoo} at 30 and 50\,cm). The improvement is the greatest for applications that perform repeated write after read operations, particularly if involving arrays (\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). This effect is seen at all distances on intermittent power. In applications with protected variables (or array elements) accessed next to each other, but residing in different SRAM or FRAM pages, \sys incurs overhead from memory virtualization that causes its performance to be comparable to (or worse than) Alpaca (\textbf{ar}, \textbf{cuckoo}). Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys's task downscaling mechanism, which was intendedly disabled for this experiment, will be able to solve this issue.

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP-to-exciter distances \{0.15, 0.3, 0.5\}\,m, compared against Alpaca (results normalized to Alpaca's performances) for ETA coalescing strategy. Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys is comparable with, or worse than, Alpaca.}
	\label{fig:runtime}
%\end{figure}
\end{wrapfigure}

@@

\textbf{Effect of Page Size on \sys Runtime.} The results (Figure~\ref{fig:page_size}, left side) show a ``bathtub curve'' in the performance of each application (the effect would be more profound with a larger set of pages than we considered), as the number of page faults varies. The data suggest that across applications there is a page size that minimizes execution time. We observe that the page size is not the same for each application, although 128\,B pages perform well for all applications.

\textbf{Page Size versus Page Faults in \sys Runtime.} The increased rate of page faults (Figure~\ref{fig:page_size}, right side) is responsible for the overhead with small page sizes; smaller pages require accessing more different pages, leading to higher paging costs. With larger page sizes, the overhead is higher than with moderate pages, too. The explanation for these higher overheads is that large pages have a higher commit cost. Even if an application accesses few memory locations, \sys pages data at full page size, degrading performance by sometimes paging in and out unnecessary data. The data reveal a reasonable default page size of 128\,B and, when developing an application, a programmer should consider varying the page size to moderate poor performance.
